Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova Remnant

### 2014-10-23 manuscript/paper-tycho.tex
Damp params plot, paper results/disc, Tycho table
Grid of profiles over damping model parameter space.
Polish text results, restructure / start fleshing discussion
Generate new set of Tycho tables (loss-lim + damped)

\shorttitle{Synchrotron Rims in Tycho's SNR}  % <~ 44 char
\shortauthors{XXX et al.}  % Max three
\slugcomment{Draft, \today}  % short title pg comment

@@

\title{Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent}

@@

\begin{abstract}
\note[Aaron]{Modified from AAS abstract - first pass update}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
models.  We are unable to distinguish between scenarios, as models for rim
widths incorporating electron cut-offs both reproduce the observed rim
drop-offs.  The best loss-limited fits require amplified magnetic fields of
$\abt200$--$1000 \muG$ and particle diffusion coefficients $\abt
1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR, whereas
magnetic damping fits permit magnetic fields of $\abt 10$--$300 \muG$ and
comparatively smaller diffusion coefficients (typically $\abt 1$--$10$).
Non-negligible diffusion coefficients, magnetic field strengths, and magnetic
damping lengthscales are somewhat degenerate in setting observed rim widths and
drop-offs.  A different approach will be needed to determine the presence of
magnetic damping downstream of supernova remnant shocks.
\end{abstract}

@@

@@

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  The
relatively strong synchrotron radiation, in conjunction with multiwavelength
spectra (radio, X-ray, gamma ray) \citep{aharonian2004, acero2010,
ackermann2013} and observations of rapid time variability \citep{uchiyama2007},
suggests that electrons are accelerated to PeV energies in young SNRs.
Although synchrotron emission due to accelerated electrons does not imply
acceleration of an unseen hadronic component, the prevailing theory of
diffusive shock acceleration (DSA) should operate on both protons and
electrons.  Efficient hadron acceleration in supernova remnant shocks is a
prime candidate source for galactic cosmic rays up to the cosmic ray spectrum's
``knee'' \citep{vink2012}.  \note[Aaron]{the discussion of hadronic
acceleration isn't really relevant, just background information}

% What can we learn from these shocks?  Why are they interesting?
Spectral and spatial measurements of synchrotron rims can constrain physical
parameters of the shock acceleration process.  Many previous workers have
inferred strong magnetic field amplification at SNR shocks, as electrons must
rapidly radiate energy to account for the thinness of observed rims
\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
synchrotron flux from supernova remnants steepens at X-ray energies
\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
spectrum as predicted by diffusive shock acceleration \citep{webb1984}.
\note[Aaron]{question: which came first?  observation of synchrotron
steepening, or explanation/prediction of electron cut-off and hence synchrotron
roll-off?  Or, even, was the electron cut-off predicted but the observable
consequence of synchrotron roll-off not recognized until observations?} Many
fundamental questions about the shock acceleration process remain to be
answered.  Under what conditions do shocks accelerate particles efficiently?
How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
relevant observations and open questions to date.  The answers to these
questions are broadly relevant to many astrophysical shocks, such as Earth's
bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
even cosmological shocks \citep{ryu2008}.
% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
% behind the shock, upstream/downstream plasma interactions and instabilities
% These in turn affect plasma, CR dynamics -- how does the shock propagate and
% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
% streaming?  How efficiently are CRs accelerated?

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We first introduce our transport models for electron advection and diffusion
with continuous synchrotron losses.  We selected and measured rim widths at
several locations around Tycho's forward shock, verifying that selected rims
are free of thermal line emission.  Using our models for particle transport
(with DSA included, to first order, in a simple exponentially cut-off injected
electron spectrum), we predict width-energy dependence in the loss-limited and
magnetic damping scenarios to obtain estimates on magnetic field strength and
diffusion coefficient magnitude.  We discuss degeneracy in our model fits and
the implications for future studies of young supernova remnant shocks.

@@

% Could just discuss one model...
We consider two particle transport models that we fit to measurements of
Tycho's thin rim widths.  We measure the rim full widths at half maximum
(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
model predictions of rim FWHMs at multiple photon energies, for various input
parameters.  The models accept four free parameters: magnetic field strength
$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
length).

We use CGS (Gaussian) units throughout.  Our presentation is somewhat
abbreviated; please refer to \citetalias{ressler2014} for a fuller review and
exposition of the transport models and relevant parameters' effect on rim
widths.

%Early workers measured filament widths of several historical supernova remnants
%and considered ...  Assuming that thin rim widths are limited by synchrotron
%energy losses (loss-limited rims), you have $l_{\mt{ad}} \propto v_d \tsynch$
%gives a magnetic field...  \citet{bamba2003, vink2003, yamazaki2004,
%ballet2006} More sophisticated models have followed, but the basic result is
%consistent -- magnetic fields are amplified, with some amount of diffusion.
%\citet{parizot2006, araya2010} consider diffusion and advection simultaneously
%with the catastrophic dump equation.  \citet{berezhko2003, berezhko2004,
%cassam-chenai2007, morlino2010, rettig2012} consider diffusion and advection
%simultaneously with the continuous loss equation instead.  DSA may be
%incorporated by direct calculation, or by assumption of a resultant electron
%spectrum and cut-off \citep[e.g.,][]{zirakashvili2007}.
%\citet{morlino2010}, and references therein, consider particle transport in the
%context of nonlinear DSA neglecting particle energy losses (as would be
%relevant for accelerated protons).  All the same principles.

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
advection and diffusion from initial injection at the remnant's forward shock
assuming 1-D steady-state plane transport, with spatially homogeneous and
isotropic diffusion, as following the equation:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
shock.  We consider only particle transport downstream of the shock ($x \geq
0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
encapsulate all assumptions about the accelerated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  More sophisticated treatments may explicitly treat magnetic
fields and diffusion across the shock, plasma streaming instabilities and
particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

% Simple model
A first approximation is to let electrons have constant energy that is dumped
catastrophically after a synchrotron timescale $\tsynch = 1/(b B^2 E)$, where
$b = 1.57 \times 10^{-3}$ in CGS units and $B$ is magnetic field (which may
vary in space as $B=B(x)$).  The sink term is $C = -f / \tsynch$, yielding:
\begin{equation} \label{eq:simp-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} +
    \frac{f}{\tau_{\mt{synch}}} = 0 .
\end{equation}
No assumptions on the injected electron source term are necessary.
\citet{parizot2006} employed this model to estimate magnetic fields, diffusion
coefficients, and electron spectrum cut-offs for several historical SNRs.
Conveniently, equation~\eqref{eq:simp-mod} has analytic solution $f \propto
\exp(-x/a)$ where $a$ is a characteristic scale length.  The thin rim FWHM
predicted by equation~\eqref{eq:simp-mod} is:
\begin{equation} \label{eq:simp-fwhm}
    w = \frac{2\beta D / v_d}{\sqrt{1 +\frac{4D}{v_d^2 \tsynch}} - 1}
\end{equation}
with $\beta$ a projection factor relating $w$ to $a$ as $w = \beta a$
\citep{berezhko2004, parizot2006}.  We take $\beta = 4.6$ assuming a spatially
exponential $f(E,x)$ and projection from a spherical shell, as derived by
\citet{ballet2006}.

% Full model
A more accurate model accounts for continuous synchrotron losses as electrons
are injected from an exponentially cut-off power-law electron distribution
(normalization $K_0$, cut-off energy $\Ecut$) and transported downstream:
\begin{align} \label{eq:full-mod}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} =\;
    &K_0 E^{-s} e^{-E/\Ecut} \delta(x) \nonumber \\
    &+ \frac{\ptl}{\ptl E} \left(bB^2E^2f\right) ;
\end{align}
see \citet{webb1984}, \citet{berezhko2004}, \citet{cassam-chenai2007},
\citet{morlino2010}, \citet{rettig2012}, and references therein.
The cut-off energy is determined by the diffusion coefficient $D$,
which we address in Section~\ref{sec:diffcoeff}.  To determine rim profiles and
widths, we first numerically solve for electron distribution $f(E,x)$ using
Green's function solutions by \citet{lerche1980} and \citet{rettig2012}; these
solutions are given by \citetalias{ressler2014} using notation similar to that
used herein \note[Aaron]{wording}.  The electron distribution may then be
integrated to obtain synchrotron emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ is one-particle synchrotron emissivity
with $K_{5/3}(z)$ a modified Bessel function of the second kind
\citep{pacholczyk1970}.  Integrating emissivity over lines of sight for a
spherical remnant yields intensity as a function of radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                    j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  A model FWHM may then be calculated
from the resulting intensity profile.

@@

% Bohm, Bohm-like, and MHD/turbulence-inspired diffusion
Much previous work has assumed Bohm-like diffusion in plasma downstream of SNR
shocks.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
equal to the gyroradius $r_g = E/(eB)$, yielding diffusion coefficient
$D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$; here $c$ is the speed of light,
$E$ is particle energy, $e$ is the elementary charge, and $B$ is magnetic
field.  Bohm-like diffusion introduces a free prefactor $\eta$ such that
$\lambda = \eta r_g$ allows for varying diffusion; however, Bohm diffusion at
$\eta = 1$ is commonly considered a lower limit on the diffusion coefficient at
all energies.
\note[Aaron]{for self-edification, any justification / derivation of Bohm
limit?  All the papers seem to take it for granted}
Different types of MHD turbulence may give rise to a non-linear energy
scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
quasi-linear approximation for particle motion,
\note[Aaron]{I don't really know what this means}
predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
Particle gyroradii larger than field coherence length may to $D \propto E^{2}$
\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing.
I have no idea what this means.}

% Define our diffusion coefficient, introduce fiducial energy
In our models, we consider a generalized diffusion coefficient with arbitrary
power-law dependence upon energy following, e.g., \citet{parizot2006}:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \frac{\eta C_d E^\mu}{B}
         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu
\end{equation}
where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has units
of $\mathrm{erg}^{1-\mu}$.
The right-hand side of equation~\eqref{eq:diffcoeff} introduces $\eta_h$, a
dimensionless diffusion coefficient scaled to the Bohm value at a fiducial
particle energy $E_h$.  Note that $\eta_h$ and $\eta$ are related as
$\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like diffusion
($\mu = 1$).

@@

\subsection{Electron cut-off}

% Electron cut-off energy
With a diffusion coefficient in hand, we determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated, so the energy spectrum drops off steeply.  The cut-off energy
adapted from \citet{parizot2006} is given as:
\begin{align} \label{eq:ecut}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
\citet{parizot2006} derive equation~\eqref{eq:ecut} in the case $\mu=1$
assuming a strong shock with compression ratio 4 and isotropic magnetic
turbulence on both sides of the shock.

As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
flux, the synchrotron roll-off frequency may provide an independent observable
to estimate shock diffusion and is given by:
\begin{align} \label{eq:rolloff}
    \nu_{\mt{cut}} =
        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
        \left(0.2657 \unit{erg^2\;G}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
        &\left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
\end{align}
In particular, this equation is independent of magnetic field $B$ for all
values of $\mu$ (but recall that the specific electron energies associated with
$\eta_2$ will depend on $B$).

% Magnetic damping
\subsection{Magnetic damping}

We also consider a magnetically damped field of form
\begin{equation}
    B(x) = B_{\mt{min}} + \left(B_0 + B_{\mt{min}}\right) \exp\left(-x / a_b\right) ,
\end{equation}
following \citet{pohl2005}.
In the full continuous energy loss model (equation~\eqref{eq:full-mod}), it
suffices to substitute $B = B(x)$ throughout; in the simpler model, $B(x)$
enters through the diffusion coefficient $D = D(E,x)$ and the analytic
expression (equation~\eqref{eq:simp-fwhm}) may no longer be valid.
Again, \citetalias{ressler2014} detail how to integrate a damped field into the
full model solutions to equation~\eqref{eq:full-mod}.

%(DRAFT) We currently do not present model fits with magnetic damping, although
%in principle they are doable.  Set up the calculation w/ a range of scale
%lengths (with $B_0$, $\eta_2$ chosen so that damping is the dominant control
%for $0.7$--$7 \unit{keV}$), and compute FWHMs and $\mE$ values?

\subsection{Width-energy dependence and some intuition} \label{sec:energydep}

As discussed in Section~\ref{sec:intro}, width-energy dependence is key to
differentiating between loss/diffusion-limited rims and magnetically damped
rims.  \citetalias{ressler2014} parameterize rim width-energy dependence in
terms of a scaling exponent $\mE$ defined by:
\begin{equation}
    w(\nu) \propto \nu^{\mE}
\end{equation}
where $w(\nu)$ is filament FWHM as a function of observed photon frequency
$\nu$.  We may refer to observed photons interchangeably by energy or frequency
$\nu$, but $E$ is reserved for electron energy.  The exponent $\mE = \mE(\nu)$
is generally energy dependent.

We may consider advective and diffusive lengthscales for electron transport,
which naturally give rise to scaling relations:
\begin{equation} \label{eq:lad}
    l_{\mt{ad}} = v_d \tsynch \propto v_d B_0^{-3/2} \nu^{-1/2}
\end{equation}
and
\begin{equation} \label{eq:ldiff}
    l_{\mt{diff}} = \sqrt{D \tsynch} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
\end{equation}
If both diffusion and magnetic field damping are negligible (whether at a small
range of, or all, electron energies) and electrons are only loss-limited as
they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$; this is the
strongest energy-dependence possible in our models.  Diffusion increases $\mE$
monotonically towards a value between $-1/4$ and $1/4$, depending on the value
of $\mu$.  In practice, $\mE$ appears to plateau at values between $-0.4$ and
$0$, with larger $\mu$ values yielding $\mE$ closer to $0$ (weaker
energy-dependence) \citepalias[Figure 3]{ressler2014}.  This may be attributed
in part to the electron energy cut-off, which limits the available electrons at
higher energies and thus thins the rims slightly, shifting $\mE$ negative
\citepalias[Figure 5]{ressler2014}.

>>>>

\shorttitle{Tycho's Synchrotron Rims (\today)}  % <~ 44 char
\shortauthors{XXX et al. (\today)}  % Max three
\slugcomment{Draft, \today}  % short title pg comment

@@

\title{Energy Dependence of Synchrotron X-Ray Rims in Tycho's Supernova
Remnant}

@@

\begin{abstract}
\note[Aaron]{Modified from AAS abstract - first pass update}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  We measured rim widths
around Tycho's supernova remnant in 5 energy bands using an archival $750
\unit{ks}$ \Chandra observation.  Rims consistently narrow with increasing
energy and are well-described by either loss-limited or magnetically damped
scenarios, hence X-ray rim widths alone cannot discriminate between models.
Loss-limited fits require amplified magnetic fields of $\abt200$--$1000 \muG$
and particle diffusion coefficients $\abt1$--$100\times$ Bohm values,
consistent with prior work on Tycho's SNR, whereas magnetic damping permits
magnetic fields of $\abt 10$--$300 \muG$ and comparatively smaller diffusion
coefficients (typically $\abt 1$--$10$).  Diffusion coefficients, magnetic
field strengths, and magnetic damping lengthscales are somewhat degenerate in
setting observed rim widths and drop-offs.  Although we cannot discriminate
from width measurements alone, a combined study of X-ray and radio profiles may
break the observed degeneracies to confirm or rule out turbulent magnetic field
damping downstream of supernova remnant shocks.
\end{abstract}

@@

% TODO terminology for "loss-limited" / "damped" / "constant field" / etc
% should be well established

@@

% What are these shock rims, what is this acceleration?
Forward shock accelerated electrons in young supernova remnants (SNRs) emit
synchrotron radiation strongly in the shock's immediate wake but quickly turn
off downstream, producing a shell-like morphology with bright X-ray and radio
rims/filaments due to line-of-sight projection \citep{koyama1995}.  The
relatively strong synchrotron radiation, in conjunction with multiwavelength
spectra (radio, X-ray, gamma ray) \citep{aharonian2004, acero2010,
ackermann2013} and observations of rapid time variability \citep{uchiyama2007},
suggests that electrons are accelerated to PeV energies in young SNRs.
Although synchrotron emission due to accelerated electrons does not imply
acceleration of an unseen hadronic component, the prevailing theory of
diffusive shock acceleration (DSA) should operate on both protons and
electrons.  Efficient hadron acceleration in supernova remnant shocks is a
prime candidate source for galactic cosmic rays up to the cosmic ray spectrum's
``knee'' \citep{vink2012}.

% What can we learn from these shocks?  Why are they interesting?
Spectral and spatial measurements of synchrotron rims can constrain physical
parameters of the shock acceleration process.  Many previous workers have
inferred strong magnetic field amplification at SNR shocks, as electrons must
rapidly radiate energy to account for the thinness of observed rims
\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
synchrotron flux from supernova remnants steepens at X-ray energies
\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
spectrum as predicted by diffusive shock acceleration \citep{webb1984}.  Many
fundamental questions about the shock acceleration process remain to be
answered.  Under what conditions do shocks accelerate particles efficiently?
How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
relevant observations and open questions to date.  The answers to these
questions are broadly relevant to many astrophysical shocks, such as Earth's
bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
even cosmological shocks \citep{ryu2008}.
% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
% behind the shock, upstream/downstream plasma interactions and instabilities
% These in turn affect plasma, CR dynamics -- how does the shock propagate and
% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
% streaming?  How efficiently are CRs accelerated?

@@

% Paper roadmap
Our procedure closely follows that of \citetalias{ressler2014}.
We selected and measured rim widths at several locations around Tycho's forward
shock, verifying that selected rims are free of thermal line emission.  Using a
model for particle transport with an exponentially cut-off injected electron
spectrum, we fit width measurements to model predictions in the loss-limited
and magnetic damping scenarios to obtain estimates on magnetic field strength
and diffusion coefficient magnitude.  We discuss degeneracy in our model fits
and the implications for future studies of young supernova remnant shocks.

@@

% Could just discuss one model...
%We consider two particle transport models that we fit to measurements of
%Tycho's thin rim widths.  We measure the rim full widths at half maximum
%(FWHMs) (Section~\ref{sec:fwhms}) and compare our measurements to the transport
%model predictions of rim FWHMs at multiple photon energies, for various input
%parameters.  The models accept four free parameters: magnetic field strength
%$B_0$, a scaled diffusion coefficient $\eta_2$, a diffusion-energy scaling
%exponent $\mu$, and a magnetic damping lengthscale $a_b$ (an $e$-folding
%length).

% Twiddle-ables in our model (the most useful part, since just modeling
% alone don't do much)
Our model fitting explores the space of varying diffusion (a bulk
representative of the underlying MHD turbulence and what have you)
and considers the two scenarios of constant magnetic field (resulting in
so-called loss-limited rims) and a damped field that falls off exponentially
behind the forward shock, as suggested by \citet{pohl2005}.
% this might go at the front before we launch into model details.

@@

% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant's forward
shock controls the synchrotron rims we see in X-ray and radio.  We assume that
diffusive shock acceleration creates a power-law distribution of electrons with
an exponential cut-off at the forward shock, located at $x = 0$ with $x > 0$
increasing downstream of the shock, given as
$f(E,x=0) = K_0 E^{-s} e^{-E/\Ecut}$.  Here $K_0$ is an arbitrary
normalization, $E$ is electron energy, and the cut-off energy $\Ecut$ is given
below in Section~\ref{sec:diffcoeff}; the spectral index $s$ is taken from
the radio index $\alpha$ as $s = 2\alpha + 1$.

All constants and equations are given in CGS (Gaussian) units.  Our
presentation is somewhat abbreviated, but a fuller exposition and literature
review is given by \citetalias{ressler2014}.

We model electron advection and diffusion downstream of the shock (i.e., for
$x>0$ only) with a 1-D steady-state plane transport equation:
\begin{equation} \label{eq:model}
    v_d \frac{\ptl f}{\ptl x}
    - \frac{\ptl}{\ptl x} \left(D\frac{\ptl f}{\ptl x}\right)
    - \frac{\ptl}{\ptl E} \left(bB^2E^2f\right)
    = K_0 E^{-s} e^{-E/\Ecut} \delta(x) ;
\end{equation}
this follows the work of \citet{webb1984, berezhko2004, cassam-chenai2007,
morlino2010, rettig2012}.  Here $f = f(E,x)$ is electron distribution as a
function of electron energy $E$ and downstream distance $x$, $D$ is the
diffusion coefficient, and $v_d$ is plasma velocity downstream of the shock.
The constant $b = 1.57 \times 10^{-3}$ in CGS units arises from synchrotron
power loss at electron energy $E$ (i.e., $\ptl E/\ptl t = b B^2 E^2$).
We have assumed isotropic diffusion and consider only processes operating
downstream of the shock.  More sophisticated treatments may explicitly treat
magnetic fields and diffusion across the shock, plasma streaming instabilities
and particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

To determine rim profiles and widths, we numerically solve for electron
distribution $f(E,x)$ using Green's function solutions by \citet{lerche1980}
and \citet{rettig2012}; the solutions are given by \citetalias{ressler2014}
using notation similar to ours.  We note, however, that the solutions for
$f(E,x)$ in equation~\eqref{eq:model} are derived assuming that $D(x) B^2(x)$
is constant \citep{lerche1980}; we will revisit this assumption further below.
% TODO give section number when you revisit this
The electron distribution may be integrated over the one-particle synchrotron
emissivity $G(y)$ to obtain the ``total'' emissivity:
\begin{equation} \label{eq:emissivity}
    j_{\nu}(x) \propto \int_0^\infty G(y) f(E,x) dE
\end{equation}
where $y \equiv \nu/(c_1 E^2 B)$ is a scaled synchrotron frequency and
$G(y) = y \int_y^\infty K_{5/3}(z) dz$ with $K_{5/3}(z)$ a modified Bessel
function of the second kind \citep{pacholczyk1970}.  Integrating emissivity
over lines of sight for a spherical remnant yields intensity as a function of
radial coordinate $r$:
\begin{equation} \label{eq:intensity}
    I_{\nu}(r) = 2 \int_0^{\sqrt{r_s^2 - r}}
                   j_{\nu} \left( r_s - \sqrt{s^2 + r^2} \right) ds
\end{equation}
where $s$ is the line-of-sight coordinate.  Finally, we compute the full width
at half maximum (FWHM) of the resulting intensity profile to compare to our
measurements of rim width.

@@

% Bohm, Bohm-like, and MHD/turbulence-inspired diffusion
Most previous work has assumed Bohm-like diffusion in plasma downstream of SNR
shocks.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
equal to the gyroradius $r_g = E/(eB)$, yielding diffusion coefficient
$D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$; here $c$ is the speed of light,
$E$ is particle energy, $e$ is the elementary charge, and $B$ is magnetic
field.  Bohm-like diffusion encapsulates diffusion scalings of $D \propto E$,
introducing a free prefactor $\eta$ such that $\lambda = \eta r_g$ allows for
varying diffusion strength.  However, Bohm diffusion at $\eta = 1$ is commonly
considered a lower limit on the diffusion coefficient at all energies.

Different types of MHD turbulence may give rise to a non-linear energy
scaling for diffusion coefficient instead \citep{giacalone1999, reynolds2004}.
Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
quasi-linear approximation for particle motion,
\note[Aaron]{I don't really know what this means}
predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
Particle gyroradii larger than field coherence length may also lead to
$D \propto E^{2}$ \note[Aaron]{Source?? Parizot mentions this in one sentence
and cites nothing.  I have no idea what this means.}

% Define our diffusion coefficient, introduce fiducial energy
In our models, we consider a generalized diffusion coefficient with arbitrary
power-law dependence upon energy following, e.g., \citet{parizot2006}:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \frac{\eta C_d E^\mu}{B}
         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu
\end{equation}
where $\mu$ parameterizes diffusion-energy scaling and $\eta$ now has units
of $\mt{erg}^{1-\mu}$.  The right-hand side of equation~\eqref{eq:diffcoeff}
introduces $\eta_h$, a dimensionless diffusion coefficient scaled to the Bohm
value at a fiducial particle energy $E_h$.  Note that $\eta_h$ and $\eta$ are
related as $\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like
diffusion ($\mu = 1$).

@@

% e- cutoff energy result
With a diffusion coefficient in hand, we may determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated to higher energies and the energy spectrum drops off steeply.  The
cut-off energy is given as:
\begin{align} \label{eq:ecut}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
This result is derived by \citet{parizot2006} for $\mu=1$ assuming a strong
shock with compression ratio 4 and isotropic magnetic turbulence on both sides
of the shock.

% srcut constraint on diffusion
As the DSA imposed electron cut-off results in a roll-off on SNR synchrotron
flux, the synchrotron roll-off frequency may provide an independent observable
to estimate shock diffusion and is given by:
\begin{align} \label{eq:rolloff}
    \nu_{\mt{cut}} =
        &c_m \left(13.3 \unit{erg}\right)^{\frac{4}{1+\mu}}
        \left(0.2657 \unit{erg^2\;G}\right)^{-\frac{1-\mu}{1+\mu}} \nonumber \\
        &\left( 100 \muG \right)^{\frac{1-\mu}{1+\mu}}
        \left( \frac{v_s}{10^8 \unit{cm/s}} \right)^{\frac{4}{1+\mu}}
        \left( \eta_2 \right)^{-\frac{2}{1+\mu}} .
\end{align}
In particular, this equation is independent of magnetic field $B$ for all
values of $\mu$ (but, recall that the specific electron energies associated
with $\eta_2$ will depend on $B$).

% Magnetic damping
\subsection{Magnetic fields and damping}

We consider two scenarios for post-shock magnetic field: (1) a constant field
$B(x) = B_0$, corresponding to the loss-limited rim scenario, and (2) an
exponentially damped field of form:
\begin{equation} \label{eq:bdamp}
    B(x) = \left(B_0 - B_{\mt{min}}\right) \exp\left(-x / a_b\right)
           + B_{\mt{min}}
\end{equation}
where $a_b$ is an $e$-folding damping lengthscale, following \citet{pohl2005}.
A typical lengthscale for $a_b$ is $10^{16}$ to $10^{17} \unit{cm}$
\citep{pohl2005}, corresponding to $\abt 0.1$--$1\%$ of Tycho's radius.
Hereafter, we report $a_b$ in units of shock radius $r_s$.

The electron cut-off energy (equation~\eqref{eq:ecut}) depends on the magnetic
field, which varies in a damped model.  For simplicity, we assume that the
shock acceleration process is set by the diffusion at the immediate shock and
so equation~\eqref{eq:ecut} stands as evaluated with magnetic field strength
$B_0$.
\note[Aaron]{Is this correct?  Can try rederiving the expression (particles
penetrate some distance downstream, then back), but I'm not sure if it's even
sensible with diffusion coefficient varying so sharply.}

\subsection{Rim width-energy dependence} \label{sec:energydep}

% Define \mE
Following \citetalias{ressler2014}, we parameterize rim width-energy dependence
in terms of a scaling exponent $\mE$ defined as:
\begin{equation}
    w(\nu) \propto \nu^{\mE}
\end{equation}
where $w(\nu)$ is filament FWHM as a function of observed photon frequency
$\nu$.  The exponent $\mE = \mE(\nu)$ is generally energy dependent.  We may
refer to observed photons interchangeably by energy or frequency $\nu$, but $E$
is reserved for electron energy.

% Intuition: transport lengthscales in the absence of damping
We may consider advective and diffusive lengthscales for electron transport,
which naturally give rise to scaling relations:
\begin{equation} \label{eq:lad}
    l_{\mt{ad}} = v_d \tsynch \propto v_d B_0^{-3/2} \nu^{-1/2}
\end{equation}
and
\begin{equation} \label{eq:ldiff}
    l_{\mt{diff}} = \sqrt{D \tsynch} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
\end{equation}
The characteristic time is the synchrotron cooling time
$\tsynch = 1 / (b B^2 E)$ with $b = 1.57 \times 10^{-3}$.
If both diffusion and magnetic field damping are negligible (whether at a small
range of, or all, electron energies) and electrons are only loss-limited as
they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$; this is the
strongest energy-dependence possible in our models.  Diffusion increases $\mE$
monotonically towards a value between $-1/4$ and $1/4$, depending on the value
of $\mu$.  In practice, $\mE$ appears to plateau at values between $-0.4$ and
$0$, with larger $\mu$ values yielding $\mE$ closer to $0$ (weaker
energy-dependence) \citepalias[Figure 3]{ressler2014}.  This may be attributed
in part to the electron energy cut-off, which limits the available electrons at
higher energies and thus thins the rims slightly, decreasing $\mE$
\citepalias[Figure 5]{ressler2014}.
